---
title: "Week 9, Day 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(PPBDS.data)
library(rstanarm)
library(tidyverse)

# There is one change to our data from Tuesday. We have a created a new
# variable: `poverty_n`, where the "n" stands for "normalized." To normalize data
# is to subtract the mean and divide by the standard deviation. This can be
# helpful. The coefficient to such a variable can be interpreted as a comparison
# between two groups, separated by a one standard deviation of the poverty
# measure.


week_9 <- kenya %>% 
  rename(reg_chg = reg_byrv13) %>% 
  filter(treatment %in% c("control", "local")) %>% 
  droplevels() %>% 
  mutate(poverty_n = (poverty - mean(poverty))/sd(poverty)) %>% 
  select(poll_station, reg_chg, treatment, poverty_n, poverty)

week_9 %>%
  filter(poll_station == "007/001")
  
```


## Scene 1

**Prompt:** Let's create a new model. Consider `reg_chg` as a function of `treatment`, `poverty_n` and the interaction between the two.

* Write the math for this model.

* Describe the population for which you are creating the model.

* Fit the  model and interpret the coefficients. Focus on the coefficient of the interaction term.

$$ regchg_i = \beta_0 + \beta_1 local_{i} + \beta_2 povertyn_{i} + \beta_3 local*povertyn_{i} + \epsilon_i$$
```{r}

fit_obj <- stan_glm(formula = reg_chg ~ treatment*poverty_n,
         data = week_9,
         refresh = 0) %>%
  print(digits = 6, details = FALSE)

# The model applies to those eligible to vote in Kenya.

# Coefficients: Small positive coefficients show a positive impact of treatment,
# poverty_n, and the confluence of the two on change in voter registration. 
# Last coefficient is showing how much change in registration changes with every increase in the poverty_n normalized rate for a treated locality. 
# The Intercept's coefficient indicates how much the change in registration increases when treatment is local and poverty_n is set to 0.

```



## Scene 2

**Prompt:** Let's begin with a question from Kenyan President Uhuru Kenyatta:

*Consider the polling station 007/001. What are the chances of an increase in registration of 4% if I were to give it the local treatment in January?*

Write a sentence or two for each of these topics:

* What would Wisdom suggest about the use of the `kenya` data to answer this question?

* Describe the ideal Preceptor Table.

* Graph the posterior probability distribution `reg_chg` if polling station 007/001 were to be assigned treatment in January.

* Answer the President's question.

```{r}

# The kenya data is fairly representative, since the applied population is a smaller
# observation from this dataset. However, disregarding the differences in poverty rates
# and other variables across the observations may render the estimate less accurate.

# The ideal Preceptor Table would record the change in registration for this 
# observation if it was both treated and not treated (control).

new_obs <- tibble(treatment = "local",
                 poverty_n = -1.608351)
pp <- posterior_predict(fit_obj, newdata = new_obs)
pp %>%
  as_tibble() %>%
  ggplot(aes(`1`)) +
  geom_histogram(aes(y = after_stat(count/sum(count))), bins = 100, alpha = 0.5, position = "identity") +
scale_y_continuous(labels = scales::percent_format()) +
  scale_x_continuous(labels = scales::percent_format()) +
  theme_classic() +
  labs(title = "Posterior Probability Distribution for Treatment",
       subtitle = "Registration will not change a significant amount if treated",
       x = "Change in Registration",
       y = "Probability")


tibble(reg_chg = pp) %>% 
  mutate(reg_chg = round(reg_chg, 2)) %>%
  mutate(ot_4 = ifelse(reg_chg == 0.04, TRUE, FALSE)) %>% 
  summarize(perc = sum(ot_4)/n())
# The odds of getting an increase in registration of 4% is about 6% if the polling
# station was to be assigned the treatment.

```



## Scene 3


**Prompt:**  President Kenyatta has another question:

*I care more about increasing registration in poor communities. For a community with poverty_n equal to 2, what would you expect the change in registration under treatment to be?*

Using the model which you created in Scene 1, create a graphic of the posterior probability distribution of the causal effect of `local` treatment in polling stations which have +2 sigma poverty rates. Note that there are two ways to do this. First, we can use a parameter approach. This is what we did in class last week. Second, we can use `posterior_epred()`, which is generally easier since it does the math for us. Use the `posterior_epred()` approach. 

```{r}
new_obs <- tibble(treatment = "local",
                 poverty_n = 2)
pe <- posterior_epred(fit_obj, newdata = new_obs)
pe %>%
  as_tibble() %>%
  ggplot(aes(`1`)) +
  geom_histogram(aes(y = after_stat(count/sum(count))), bins = 100, alpha = 0.5, position = "identity") +
scale_y_continuous(labels = scales::percent_format()) +
  scale_x_continuous(labels = scales::percent_format()) +
  theme_classic() +
  labs(title = "Posterior Probability Distribution for Treatment",
       x = "Change in Registration",
       y = "Probability")

posterior_interval(pe, prob = 0.95)
# The chance in registration under treatment would fall between 5.1% to 7.2%
# for communities with a poverty_n equal to 2.
```


